Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection

### 2019-05-25 reports/paper1/paper.tex
Revise paper

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing. Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features. To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection. A 3D printed sample was manufactured with voids to see if they can be detected. The x-ray acquisition was compared with a simulation of that scan under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved. Voids with diameters in the order of millimetres were detectable.
\end{abstract}

@@

The projection of the 3D printed sample was obtained and repeated 20 times at a fixed angle. The 20 projections were spilt into 2. 19 random projections were held out. The remaining projection was used to compare with the simulation using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. In the \emph{aRTist} simulation, the software did a simulation as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection.

@@

Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the projection and the \emph{aRTist} projection. A disagreement too big will classify that pixel as a positive result. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.

The variance model, $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated projections of the sample. These replicated projections were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link. The variance was predicted using the grey value in the \emph{aRTist} projection as the predictor variable when working out the test statistics.

@@

In the experiment with the 3D printed sample, the x-ray projection was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the 3D printed sample. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. The resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.

@@

The empirical null filter caters for inaccuracies made by \emph{aRTist} and voids in the order of millimetres were detectable. This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference. In the experiments, it was found that the FDR level is preserved after filtering.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Timings when filtering a $\SI{256}{px}\times \SI{256}{px}$ image. The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note that the $y$-axis changes scale. The box plot summarise 100 repeated measurements of the timings.}
  \label{fig:inference_timing}
\end{figure*}

>>>>

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing. Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features. To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection. A 3D printed sample was manufactured with voids to see if they can be detected. The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved. Voids with diameters in the order of millimetres were detectable.
\end{abstract}

@@

The projection of the sample was obtained and repeated 20 times at a fixed angle. The 20 projections were spilt into 2. 19 random projections were held out. The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
CAD of the sample \citep{bellon2011simulation, deresch2012simulating}. \emph{aRTist} was used to obtained a simulation projection as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection. A shading correction was applied to the simulated projection using a flat black image and a simulated white image.

@@

Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the projection and the simulated projection. A disagreement too big will classify that pixel as a positive result. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.

The variance model, $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated projections of the sample. These replicated projections were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link. The variance was predicted using the grey value in the simulated projection as the predictor variable when working out the test statistics.

@@

In the experiment with the 3D printed sample, the x-ray projection was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the sample. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. The resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.

@@

The empirical null filter catered for inaccuracies made by \emph{aRTist} and voids in the order of millimetres were detectable. This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference. In the experiments, it was found that the FDR level is preserved after filtering.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Timings when filtering a $\SI{256}{px}\times \SI{256}{px}$ image. The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note that the $y$-axis changes scale. The box plot summarise the 100 repeated measurements of the timings.}
  \label{fig:inference_timing}
\end{figure*}
